Hypertension and microbiome

### 2019-08-07 articletwo.Rmd
Fixing core level calculations

At species level meta has dimensions (`r dim(meta(pseq.species))`) and
there ntaxa is `r ntaxa(pseq.species)`, and at genus level meta has
dimensions (`r dim(meta(pseq.genus))`) and there ntaxa is 
`r ntaxa(pseq.genus)`.

@@

```{r maaslin runs, results = 'hide'} 
 pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)

if (!file.exists("rds/maaslin.rds")) {
     maaslin <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = var.BP,
                                    forced = var.CL,
                              taxa = taxa(pseq.genus.core))

>>>>

At species level meta has dimensions (`r dim(meta(pseq.species))`) and
there ntaxa is `r ntaxa(pseq.species)`. At genus level meta has
dimensions (`r dim(meta(pseq.genus))`) and there ntaxa is 
`r ntaxa(pseq.genus)`.

```{r defining genus core}
pseq.genus.core <- microbiome::transform(pseq.genus, "compositional") %>%
    core(detection = 0.0001, prevalence = 0.01)
```

At genus-core level meta has dimensions (`r dim(meta(pseq.genus.core))`) 
and there ntaxa is `r ntaxa(pseq.genus.core)`.

@@

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
     maaslin <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = var.BP,
                                    forced = var.CL,
                              taxa = taxa(pseq.genus.core))
